Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-07-25 text/manuscript-full-KS.qmd
add figure notes

```{=tex}
\endgroup
\doublespacing
\clearpage
```
<!-- TABLES -->

@@

@@

@@

@@

@@

@@

@@

```{r fig-dallas-maps, echo = FALSE, fig.align = 'center', fig.cap = "Dallas-Forth Worth Geomarkets, Total Population 1980-2020", out.width = "100%"}
knitr::include_graphics('./../assets/images/dallas_maps.png')
#knitr::include_graphics('./../../outputs/figures/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

@@

@@

@@

@@

```{r fig-la-maps, echo = FALSE, fig.align = 'center', fig.cap = "Los Angeles Geomarkets, Total Population 1980-2020", out.width = "100%"}
knitr::include_graphics('./../assets/images/la-maps.png')
#knitr::include_graphics('./../../outputs/figures/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

@@

@@

@@

@@

>>>>

```{=tex}
\endgroup
\clearpage
\singlespacing
```
<!-- TABLES -->

@@

```{=tex}
\clearpage
```

@@

**Note**: Race/ethnicity categories not available in 1980 Census: Asian, non-Hispanic; Two+ races, non-Hispanic; NHPI, non-Hispanic; AIAN non-Hispanic

```{=tex}
\clearpage
```

@@

**Note**: Household income measured using 2024 CPI

```{=tex}
\clearpage
```

@@

**Note**: Excludes students with missing values for race. Order number 392833 (ordered 7/10/2018): HS class 2019 OR 2020; state = IL; SAT 1020 - 1150; GPA B- to A+. Order number 487984 (ordered 7/19/2019): HS class 2020 OR 2021; state = IL; SAT 1020 - 1150; GPA B- to A+. Order number 392834 (ordered 7/10/2018): HS class 2019 OR 2020; state = IL; SAT 1160 - 1300. Order number 488035 (ordered 7/19/2019): HS class 2019 OR 2020; state = IL; SAT 1160 - 1300; GPA B- to A+. Order number 392835 (ordered 7/9/2018): HS class 2019 OR 2020; state = IL; SAT 1310 - 1600; GPA B- to A+. Order number 488053 (ordered 7/19/2019): HS class 2020 OR 2021; state = IL; SAT 1310 - 1600; GPA B- to A+.

```{=tex}
\clearpage
```

@@

**Note**: Excludes students with missing values for race. Order number 392834 (ordered 7/10/2018): HS class 2019 OR 2020; state = IL; SAT 1160 - 1300. Order number 488035 (ordered 7/19/2019): HS class 2019 OR 2020; state = IL; SAT 1160 - 1300; GPA B- to A+.

```{=tex}
\clearpage
```

@@

**Note**: Excludes students with missing values for firstgen. Order number 392834 (ordered 7/10/2018): HS class 2019 OR 2020; state = IL; SAT 1160 - 1300. Order number 488035 (ordered 7/19/2019): HS class 2019 OR 2020; state = IL; SAT 1160 - 1300; GPA B- to A+.

```{=tex}
\clearpage
```

@@

**Note**: Excludes students who have missing values for race or parental education. Order number 392834 (ordered 7/10/2018): HS class 2019 OR 2020; state = IL; SAT 1160 - 1300. Order number 488035 (ordered 7/19/2019): HS class 2019 OR 2020; state = IL; SAT 1160 - 1300; GPA B- to A+.

```{=tex}
\clearpage
```

```{r fig-dallas-maps, echo = FALSE, fig.align = 'center', fig.cap = "Dallas-Forth Worth Geomarkets, Total Population 1980-2020", out.width = "95%"}
knitr::include_graphics('./../assets/images/dallas_maps.png')
#knitr::include_graphics('./../../outputs/figures/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

```{=tex}
\clearpage
```

@@

**Note**: Excludes students with missing values for race. Order number 448922 (ordered 1/9/2019): HS class 2020; selected Geomarkets; PSAT 1070 - 1180. Order number 448427 (ordered 1/8/2019): HS class 2020; selected Geomarkets; PSAT 1190 - 1260. Order number 448440 (ordered 1/8/2019): HS class 2020; selected Geomarkets; PSAT 1270 - 1520.

```{=tex}
\clearpage
```

@@

**Note**: Excludes students with missing values for race. Order number 448427 (ordered 1/8/2019): HS class 2020; selected Geomarkets; PSAT 1190 - 1260.

```{=tex}
\clearpage
```

@@

**Note**: Excludes students with missing values for firstgen. Order number 448427 (ordered 1/8/2019): HS class 2020; selected Geomarkets; PSAT 1190 - 1260.

```{=tex}
\clearpage
```

@@

**Note**: Excludes students who have missing values for race or parental education. Order number 448427 (ordered 1/8/2019): HS class 2020; selected Geomarkets; PSAT 1190 - 1260.

```{=tex}
\clearpage
```

```{r fig-la-maps, echo = FALSE, fig.align = 'center', fig.cap = "Los Angeles Geomarkets, Total Population 1980-2020", out.width = "95%"}
knitr::include_graphics('./../assets/images/la-maps.png')
#knitr::include_graphics('./../../outputs/figures/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

```{=tex}
\clearpage
```

@@

**Note**: Excludes students with missing values for race. Order number 448375 (ordered 1/8/2019): HS class 2020; State = CA; PSAT 1070 - 1180. Order number 546954 (ordered 1/6/2020): HS class 2021; State = CA; PSAT 1070 - 1180. Order number 448420 (ordered 1/8/2019): HS class 2020 OR 2021; State = CA; PSAT 1190 - 1260. Order number 546946 (ordered 1/6/2020): HS class 2021 OR 2022; State = CA; PSAT 1190 - 1260. Order number 448374 (ordered 1/8/2019): HS class 2020 OR 2021; State = CA; PSAT 1270 - 1520. Order number 546945 (ordered 1/6/2020): HS class 2021 OR 2022; State = CA; PSAT 1270 - 1520.

```{=tex}
\clearpage
```

@@

**Note**: Excludes students with missing values for race. Order number 448420 (ordered 1/8/2019): HS class 2020 OR 2021; State = CA; PSAT 1190 - 1260. Order number 546946 (ordered 1/6/2020): HS class 2021 OR 2022; State = CA; PSAT 1190 - 1260.

```{=tex}
\clearpage
```

@@

**Note**: Excludes students with missing values for firstgen. Order number 448420 (ordered 1/8/2019): HS class 2020 OR 2021; State = CA; PSAT 1190 - 1260. Order number 546946 (ordered 1/6/2020): HS class 2021 OR 2022; State = CA; PSAT 1190 - 1260.

```{=tex}
\clearpage
```

@@

**Note**: Excludes students who have missing values for race or parental education. Order number 448420 (ordered 1/8/2019): HS class 2020 OR 2021; State = CA; PSAT 1190 - 1260. Order number 546946 (ordered 1/6/2020): HS class 2021 OR 2022; State = CA; PSAT 1190 - 1260.
